\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2022-12-01 doc/USER_MANUAL/07_adjoint_simulations.tex
user manual updated - minor updates

Instead of the kernels for the isotropic wave speeds, you can also
compute the kernels for the 21 independent components $C_{IJ},\, I,J=1,...,6$
(using Voigt's notation) of the elastic tensor in the cartesian coordinate
system. This is done by setting \texttt{ANISOTROPIC\_KL} \texttt{=}
\texttt{.true.} in \texttt{DATA/Par\_file} before compiling the package.
The definition of the parameters $C_{IJ}$ in terms of the corresponding
components $c_{ijkl},ijkl,i,j,k,l=1,2,3$ of the elastic tensor in
cartesian coordinates follows \citet{ChTr07}. The 21 anisotropic
kernels are saved in the \texttt{LOCAL\_PATH} in one file with the
name of \texttt{proc??????\_cijkl\_kernel.bin} (with \texttt{proc??????}
the processor number). The output kernels correspond to absolute perturbations
$\delta C_{IJ}$ of the elastic parameters and their unit is in $s/GPa/km^{3}$.
For consistency, the output density kernels with this option turned
on are for a perturbation $\delta\rho$ (and not $\frac{\delta\rho}{\rho}$)
and their unit is in s / (kg/m$^{3}$) / km$^{3}$. These `primary'
anisotropic kernels can then be combined to obtain the kernels for
different parameterizations of anisotropy. This can be done, for example,
when combining the kernel files from slices into one mesh file (see
Section~\ref{sec:Finite-Frequency-Kernels}).\newline

>>>>

Instead of the kernels for the isotropic wave speeds, you can also
compute the kernels for the 21 independent components $C_{IJ},\, I,J=1,...,6$
(using Voigt's notation) of the elastic tensor in the cartesian coordinate
system. This is done by setting \texttt{ANISOTROPIC\_KL} \texttt{=}
\texttt{.true.} in \texttt{DATA/Par\_file} before compiling the package.
The definition of the parameters $C_{IJ}$ in terms of the corresponding
components $c_{ijkl},ijkl,i,j,k,l=1,2,3$ of the elastic tensor in
cartesian coordinates follows \citet{ChTr07}. The 21 anisotropic
kernels are saved in the \texttt{LOCAL\_PATH} as 21 files with names 
\texttt{proc??????\_c??\_kernel.bin} (with \texttt{proc??????}
the processor number). The output kernels correspond to absolute perturbations
$\delta C_{IJ}$ of the elastic parameters and their unit is in $s/GPa/km^{3}$.
For consistency, the output density kernels with this option turned
on are for a perturbation $\delta\rho$ (and not $\frac{\delta\rho}{\rho}$)
and their unit is in s / (kg/m$^{3}$) / km$^{3}$. These `primary'
anisotropic kernels can then be combined to obtain the kernels for
different parameterizations of anisotropy. This can be done, for example,
when combining the kernel files from slices into one mesh file (see
Section~\ref{sec:Finite-Frequency-Kernels}).\newline

### 2022-12-01 doc/USER_MANUAL/14_post_processing.tex
user manual updated - minor updates

You do have further options to change this default output behavior,
given in the \texttt{DATA/Par\_file}:
\begin{description}
\item [{\texttt{USE\_BINARY\_FOR\_SEISMOGRAMS}}] Set to \texttt{.true.} to have seismograms
written out in binary format.
\item [{\texttt{WRITE\_SEISMOGRAMS\_BY\_MAIN}}] Set to \texttt{.true.}
to have only the main process writing out seismograms. This can
be useful on a cluster, where only the main process node has access
to the output directory.
\item [{\texttt{USE\_OUTPUT\_FILES\_PATH}}] Set to \texttt{.false.} to
have the seismograms output to \texttt{LOCAL\_PATH} directory specified
in the main parameter file \texttt{DATA/Par\_file}. In this case,
you could collect the synthetics onto the frontend using the \texttt{collect\_seismo\_lsf\_multi.pl}
script located in the \texttt{utils/Cluster/lsf/} directory. The usage
of the script would be e.g.:

\begin{verbatim}
collect_seismo.pl machines DATA/Par_file
\end{verbatim}

\end{description}

where \texttt{machines} is a file containing the node names and \texttt{DATA/Par\_file}
the parameter file used to extract the \texttt{LOCAL\_PATH} directory
used for the simulation.

>>>>

You do have further options to change this default output behavior,
given in the \texttt{DATA/Par\_file}:
\begin{description}
\item [{\texttt{USE\_BINARY\_FOR\_SEISMOGRAMS}}] Set to \texttt{.true.} to have seismograms
written out in binary format.
\item [{\texttt{WRITE\_SEISMOGRAMS\_BY\_MAIN}}] Set to \texttt{.true.}
to have only the main process writing out seismograms. This can
be useful on a cluster, where only the main process node has access
to the output directory.
\end{description}
